Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-17 Docs/Paper/LaTex/template.tex
more comments

\begin{abstract}
We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open MultiProcessing. The multi-core SMT-based BMC approach allows initializing many verification instances based on processors cores numbers available to the model checker. Each instance checks for a different optimum value until the optimization problem is satisfied. The goal is to show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach. We compare the experimental results of our proposed approach with Integer Linear Programming and the Genetic Algorithm.
\keywords{hardware-software co-design \and hardware-software partitioning\and optimization\and model checking\and multi-core\and OpenMP }
\end{abstract}

@@

\textcolor{Red}{Here, we will explore the explore the availability of multi-core processors, in particular SMT methods are used to analyse the partition of HW-SW, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, the results will be compared with vZ tool of Microsoft that is in the state of art [32], besides of the improved version of the search by HW-SW to multi-core processors.} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems. We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14]. As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.

>>>>

\begin{abstract}
\textcolor{blue}{Atualizar o abstract para descrever brevemente os novos algoritmos desenvolvidos}
We present an alternative approach to solve the hardware (HW) and software (SW) partitioning problem, which uses Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) in conjunction with a multi-core support using Open MultiProcessing. The multi-core SMT-based BMC approach allows initializing many verification instances based on processors cores numbers available to the model checker. Each instance checks for a different optimum value until the optimization problem is satisfied. The goal is to show that multi-core model-checking techniques can be effective, in particular cases, to find the optimal solution of the HW-SW partitioning problem using an SMT-based BMC approach. We compare the experimental results of our proposed approach with Integer Linear Programming and the Genetic Algorithm.
\keywords{hardware-software co-design \and hardware-software partitioning\and optimization\and model checking\and multi-core\and OpenMP }
\end{abstract}

@@

\textcolor{blue}{Deve-se citar as referencias usando o comando cite do latex}

\textcolor{Red}{\textcolor{blue}{Descrever brevemente o funcionamento dos algortimos propostos} Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods applied to the HW-SW partition propose are proposed, then the results are compared using ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and the vZ tool that is a state-of-art optimization tool [32].} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems. We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14]. As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.
